Utilizing Parallel Workers: \\LLVM's Vectorization Plan

### 2024-11-23 paper/paper.tex
paper

\subsubsection{VPlan and Integration with LV}
Setting up and integrating the VPlan structure into LV has seen tremendous effort over the last 
few years. Florian Hahn presented future directions for 
VPlan~\cite{llvmvplanupdate}, which mostly revolve around transforming more LV-based decisions into
explicit VPlan-to-VPlan transformations. Additionally, the old legacy LV cost model still influences 
many cost model-related decisions. However, the transition to a VPlan-based cost model has already 
started.

@@

\section{Related Work}
\label{sec:relatedwork}
Besides the main llvm-project's upstream there are many different projects making use of or extending
LLVM's toolchain.

>>>>

\subsubsection{VPlan and Integration with LV}
Setting up and integrating the VPlan structure into LV has seen tremendous effort over the last 
few years. Florian Hahn presented future directions for 
VPlan~\cite{llvmvplanupdate}, which mostly revolve around transforming more LV-based decisions into
explicit VPlan-to-VPlan transformations. Additionally, the legacy LV cost model still influences 
many cost model-related decisions. However, the transition to a VPlan-based cost model has already 
started.

@@

\section{Related Work}
\label{sec:relatedwork}
Next to the main llvm-projects upstream, many projects are using or extending the LLVM toolchain.

One such project that also tries to enable auto-vectorization support for inner-, outer-loop, and 
whole-function vectorization is the region vectorizer from the University Saarland~\cite{rv}.
This region-vectorizer implements partial control-flow linearization~\cite{10.1145/3192366.3192413}
and a divergence analysis that can handle unstructured CFGs. There has been an effort to partially
implement this control-flow linearization and divergence analysis into LLVM's 
upstream~\cite{rvproposal,rvproposaldep}.
